---
title: "Survey demography"
author: "Thomas Klebel"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggchicklet)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, dpi = 300)

extrafont::loadfonts(device = "win")

theme_set(hrbrthemes::theme_ipsum_rc(base_family = "Hind"))

df <- targets::tar_read(clean_data)
wb_countries <- targets::tar_read(wb_countries)

custom_blue <- "#3792BD"
```


# Gender (X84)

```{r}
df %>% make_table(X84, label = "Gender")
```
# Academic role (X85)
```{r}
make_table(df, X85, label = "Academic role")
```

Merge junior roles

```{r}
df %>% 
  mutate(X85 = case_when(str_detect(X85, "Post-doc") ~ "Prae/Post-doc",
                         str_detect(X85, "Doctoral") ~ "Prae/Post-doc",
                         TRUE ~ X85)) %>% 
  make_table(X85, label = "Academic role")
```

# Year of first academic publication (X87)
```{r academic-age}
df %>% 
  # fix mis-typed input
  mutate(X87 = case_when(X87 == 19999 ~ 1999,
                         X87 == 84 ~ 1984,
                         TRUE ~ X87)) %>% 
  ggplot(aes(X87)) +
  geom_histogram(binwidth = 2, fill = custom_blue) +
  labs(x = "Year of first publication", y = NULL)
```

# Type of instiution (X88 + X89)
Q: "How would you characterise your institution?"
```{r}
df %>% 
  make_table(X88)
```

Q: "How would you characterise your institution?"

```{r}
df %>% 
  count(X89) %>% 
  drop_na() %>% 
  knitr::kable()
```
# Disciplines (X90 + X91)
```{r}
df %>% 
  make_table(X90)
```

```{r}
df %>% 
  count(X91) %>% 
  drop_na() %>% 
  knitr::kable()
```


Disciplines were manually grouped by using the topics from the Web of Science:
https://images.webofknowledge.com/images/help/WOS/hp_research_areas_easca.html


```{r}
df %>% 
  drop_na(disciplines_recoded_wos) %>% # there is one missing case
  make_table(disciplines_recoded_wos)
```

```{r disciplines}
plot_bar(df, disciplines_recoded_wos, nudge_y = .01) +
  labs(caption = "n = 197")
```

# Type of contract
```{r}
# X15 = Are you on a limited-term contract?
df %>% make_table(X15)
```
```{r}
df %>% 
  filter(X15 == "Other") %>% 
  select(X16)
# one of the "others" is technically on a permanent contract
```

```{r}
total_unlimited <- {df %>% filter(X15 == "No") %>% nrow()} + 1
share <- total_unlimited/nrow(df)

glue::glue("Number and share of researchers on unlimited contract: 
           {total_unlimited} ({scales::percent(share, .1)})")
```


# Country
```{r}
# checking for others
stopifnot(identical(nrow(filter(df, X12 == "Other")), 0L))

# n for country
nrow(df)

# inspect country
df %>% make_table(X12, label = "Country")
```

```{r}
# number of countries
df %>% 
  summarise(n_countries = n_distinct(X12))
```


```{r}
# lumping together
country <- df %>% 
  mutate(country_lumped = fct_lump_min(X12, min = 4)) %>% 
  select(X12, country_lumped)
```

```{r country, fig.width=8, fig.height=5}
country %>% 
  count(country_lumped) %>% 
  mutate(prop = n / sum(n),
         labels = scales::percent(prop, .1)) %>% 
  mutate(country_ordered = fct_reorder(country_lumped, n, .fun = max,
                                       .desc = TRUE) %>% 
           fct_relevel("Other", after = Inf)) %>% 
  ggplot(aes(country_ordered, prop)) +
  geom_text(aes(label = labels), nudge_y = .01, size = 3.8, family = "Hind") +
  geom_col(width = .7, fill = custom_blue) +
  # geom_chicklet(width = .8, radius = unit(7, "pt")) +
  scale_x_discrete(guide = guide_axis(angle = 45, )) +
  scale_y_continuous(labels = scales::percent) +
  labs(x = NULL, y = NULL) +
  hrbrthemes::theme_ipsum_rc(base_family = "Hind", grid = "Y")
```

Alternative with dotplot

```{r country-dotplot, fig.height=5, fig.width=7}
plot_bar(country, country_lumped, nudge_y = .005, last_val = "Other")
```


Further classify countries per WP categories. Categories from: 
https://datahelpdesk.worldbank.org/knowledgebase/articles/906519-world-bank-country-and-lending-groups

```{r}
# computations were moved higher up the pipeline
```

```{r country-grouped-percentage, fig.width=6, fig.height=5}
df %>% 
  count(Region) %>% 
  mutate(prop = n / sum(n),
         labels = scales::percent(prop, .1)) %>% 
  mutate(country_ordered = fct_reorder(Region, n, .fun = max,
                                       .desc = TRUE)) %>% 
  ggplot(aes(country_ordered, prop)) +
  geom_text(aes(label = labels), nudge_y = .03, size = 3.8, family = "Hind") +
  geom_col(width = .7, fill = custom_blue) +
  # geom_chicklet(width = .8, radius = unit(7, "pt")) +
  scale_x_discrete(guide = guide_axis(angle = 45, )) +
  scale_y_continuous(labels = scales::percent) +
  labs(x = NULL, y = NULL) +
  hrbrthemes::theme_ipsum_rc(base_family = "Hind", grid = "Y")
```

alternative with n
```{r country-grouped-n, fig.width=6, fig.height=5}
df %>% 
  count(Region) %>% 
  mutate(prop = n / sum(n),
         labels = n) %>% 
  mutate(country_ordered = fct_reorder(Region, n, .fun = max,
                                       .desc = TRUE)) %>% 
  ggplot(aes(country_ordered, prop)) +
  geom_text(aes(label = labels), nudge_y = .03, size = 3.8, family = "Hind") +
  geom_col(width = .7, fill = custom_blue) +
  # geom_chicklet(width = .8, radius = unit(7, "pt")) +
  scale_x_discrete(guide = guide_axis(angle = 45, )) +
  scale_y_continuous(labels = scales::percent) +
  labs(x = NULL, y = NULL) +
  hrbrthemes::theme_ipsum_rc(base_family = "Hind", grid = "Yy")
```

```{r country-grouped-lollipop}
plot_bar(df, Region)
```

