---
title: "Institutional context"
author: "Thomas Klebel"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggchicklet)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, dpi = 300)

theme_set(hrbrthemes::theme_ipsum_rc(base_family = "Hind"))

df <- targets::tar_read(shareable_data)
var_overview <- targets::tar_read(var_overview)
```


# Do you see yourself working at the same institution in 5 years? (X17)
```{r}
df %>% make_table(X17)
df %>%
  count(X18)
```

# Do you intend to apply for a promotion within the next 5 years? (X19)
```{r}
df %>% make_table(X19)
```

# Combine them
```{r institutional-context, fig.width=8, fig.height=3}
pdata <- df %>% 
  select(X17, X19) %>% 
  pivot_longer(everything(), names_to = "var", values_to = "val") %>% 
  count(var, val) %>% 
  group_by(var) %>% 
  mutate(percent = n/sum(n),
         val = fct_relevel(val, "Yes", "No", "Other", "I don't know", 
                           "Not applicable"))

pdata <- pdata %>% 
  mutate(var = case_when(
    var == "X17" ~ "Do you see yourself working at the same institution in 5 years?",
    TRUE ~ "Do you intend to apply for a promotion within the next 5 years?"),
         var = str_wrap(var, 30))

pdata %>% 
  ggplot(aes(var, percent, fill = val)) +
  geom_chicklet(width = .7) +
  coord_flip() +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = c(
    "Yes" = "#B96FB0",
    "No" = "#54984E",
    "Other" = "#E0C47C",
    "I don't know" = "grey80", #C9D1F9
    "Not applicable" = "#1C94BB"
  )) +
  labs(x = NULL, y = NULL, fill = NULL) +
  theme(legend.position = "top")
```

```{r}
pdata %>% 
  mutate(var = str_replace_all(var, "\\n", " ")) %>% 
  arrange(var, val) %>% 
  knitr::kable()
```

# Familiarity with promotion policy (X21, X22)

- "For each of the statements below provide your personal level of agreement or disagreement: [I know where to find the promotion policy relevant to my current career stage as a researcher (e.g. institution’s website, intranet or handbook)]"

```{r}
df %>% 
  filter(X21 != "Not applicable") %>% 
  make_table(X21, sort = FALSE)
```


- For each of the statements below provide your personal level of agreement or disagreement: [I am familiar with the promotion policy that applies to my current career stage]

```{r}
df %>% 
  filter(X22 != "Not applicable") %>% 
  make_table(X22, sort = FALSE)
```

## Combine both

```{r knowledge-of-prt-policies, fig.width=8, fig.height=3.5}
pdata <- df %>% 
  select(X21, X22) %>% 
  pivot_longer(everything(), names_to = "var", values_to = "val") %>% 
  filter(val != "Not applicable") %>% 
  count(var, val) %>% 
  group_by(var) %>% 
  mutate(percent = n/sum(n),
         val = fct_relevel(val, "Completely agree", "Agree", 
                           "Neither agree nor disagree", "Disagree",
                           "Completely disagree", "I don't know"))

pdata <- pdata %>% 
  mutate(var = case_when(
    var == "X21" ~ "I know where to find the promotion policy relevant to my current career stage.",
    TRUE ~ "I am familiar with the promotion policy that applies to my current career stage"),
         var = str_wrap(var, 30))

pdata %>% 
  ggplot(aes(var, percent, fill = val)) +
  geom_chicklet(width = .7) +
  coord_flip() +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = c("#B96FB0", "#F9AEEF", "#E0C47C", "#94D790",
                               "#54984E", "grey80")) +
  guides(fill = guide_legend(byrow = TRUE)) +
  labs(x = NULL, y = NULL, fill = NULL) +
  theme(legend.position = "top")
```

```{r}
pdata %>%
  mutate(var = str_replace_all(var, "\\n", " ")) %>% 
  arrange(var, val) %>% 
  knitr::kable()
```


# Gender and other equality
## Institutional opinion
```{r}
base <- df %>%
  select(X1, X44:X45) %>%
  pivot_longer(-X1, names_to = "var", values_to = "val") 

# get labels
labels <- var_overview %>%
  filter(var_id %in% c("X44", "X45")) %>%
  mutate(label = str_extract(var_full, "(?<=\\[).*?(?=\\s?\\])")) %>%
  select(var_id, label)

combined <- base %>%
  left_join(labels, by = c("var" = "var_id")) %>%
  select(-var)

pdata <- combined %>% 
  count(label, val) %>% 
  make_proportion(group = label, var = val) %>% 
  mutate(val = fct_relevel(
    val,
    "Completely agree", "Agree", "Neither agree nor disagree", "Disagree", 
    "Completely disagree", "I don't know", "Not applicable"
  ))

```
```{r}
pdata %>% 
  select(-order) %>% 
  arrange(label, val) %>% 
  knitr::kable()
```


```{r equality-institution, fig.width=9, fig.height=4}
pdata %>% 
  ungroup() %>% 
  mutate(label = str_wrap(label, 40)) %>% 
  ggplot(aes(label, prop, fill = val)) +
  geom_chicklet(width = .7) +
  coord_flip() +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = c("#B96FB0", "#F9AEEF", "#E0C47C", "#94D790",
                               "#54984E", "grey80", "#1C94BB")) +
  guides(fill = guide_legend(byrow = TRUE)) +
  labs(x = NULL, y = NULL, fill = NULL) +
  theme(legend.position = "top")
```

## Personal opinion

```{r}
base <- df %>%
  select(X1, X66:X67) %>%
  pivot_longer(-X1, names_to = "var", values_to = "val") 

# get labels
labels <- var_overview %>%
  filter(var_id %in% c("X66", "X67")) %>%
  mutate(label = str_extract(var_full, "(?<=\\[).*?(?=\\s?\\])")) %>%
  select(var_id, label)

combined <- base %>%
  left_join(labels, by = c("var" = "var_id")) %>%
  select(-var)

pdata <- combined %>% 
  count(label, val) %>% 
  make_proportion(group = label, var = val) %>% 
  mutate(val = fct_relevel(
    val,
    "Completely agree", "Agree", "Neither agree nor disagree", "Disagree", 
    "Completely disagree", "I don't know", "Not applicable"
  ))

```
```{r}
pdata %>% 
  select(-order) %>% 
  arrange(label, val) %>% 
  knitr::kable()
```


```{r equality-personal, fig.width=9, fig.height=4}
pdata %>% 
  ungroup() %>% 
  mutate(label = str_wrap(label, 40)) %>% 
  ggplot(aes(label, prop, fill = val)) +
  geom_chicklet(width = .7) +
  coord_flip() +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = c("#B96FB0", "#F9AEEF", "#E0C47C", "#94D790",
                               "#54984E", "grey80", "#1C94BB")) +
  guides(fill = guide_legend(byrow = TRUE)) +
  labs(x = NULL, y = NULL, fill = NULL) +
  theme(legend.position = "top")
```
