---
title: "Attitudes towards criteria"
author: "Thomas Klebel"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggchicklet)
library(patchwork)
library(janitor)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, dpi = 300)

extrafont::loadfonts(device = "win")

theme_set(hrbrthemes::theme_ipsum_rc(base_family = "Hind"))

df <- targets::tar_read(shareable_data)
var_overview <- targets::tar_read(var_overview)
expanded_labels <- targets::tar_read(expanded_labels)
custom_blue <- "#3792BD"
```


# Institutional view: X23 - X41
"According to your institutional policies, how important are the following research activities in making promotion decisions in relation to your current career stage?  [Publishing a large number of research articles]"

etc.

```{r}
step1 <- df %>% 
  select(X23:X41) %>% 
  pivot_longer(everything(), names_to = "var", values_to = "val") %>%
  count(var, val)

# remove dont knows and not applicables
nas <- step1 %>% 
  filter(val %in% c("I don't know", "Not applicable"))

pdata <- step1 %>% 
  anti_join(nas) %>% 
  mutate(val = fct_relevel(val, "Very important", "Somewhat important",
                           "Neither important nor unimportant", 
                           "Somewhat unimportant", "Very unimportant")) %>% 
  make_proportion(group = var, var = val, order_string = "\\simportant$")


# get labels
labels <- var_overview %>% 
  filter(var_id %in% paste0("X", 23:41)) %>% 
  mutate(label = str_extract(var_full, "(?<=\\[).*?(?=\\s?\\])"),
         # clean up labels
         label = str_remove(label, "\\(.*"),
         label = str_remove(label, ", as assessed .*")) %>% 
  select(var_id, label)

pdata_institution <- pdata %>% 
  left_join(labels, by = c("var" = "var_id"))
```

```{r}
pdata_institution %>% 
  ungroup() %>% 
  arrange(desc(order), val) %>% 
  mutate(prop = scales::percent(prop, accuracy = .1),
         summary = glue::glue("{n} ({prop})")) %>% 
  select(variable = label, value = val, summary) %>%
  pivot_wider(names_from = value, values_from = summary,
              values_fill = "0 (0.0%)", names_sort = TRUE) %>% 
  knitr::kable()
```


```{r institutional-attitudes, fig.width=10, fig.height=7}
# colours came from `RColorBrewer::brewer.pal("PiYG", n = 5)`, but with yellow 
# as the midpoint
# new colours: 
purple <- c('#F9AEEF', '#B96FB0') # light, dark
green <- c('#94D790', "#54984E") # light, dark
blue <- c('#86CFFB', '#3792BD') # light, dark
midpoint <- "#E0C47C"

p1 <- pdata_institution %>% 
  ggplot(aes(fct_reorder(label, order), prop, fill = val)) +
  geom_chicklet(width = .7) +
  coord_flip() +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = c("#B96FB0", "#F9AEEF", "#E0C47C", "#94D790",
                               "#54984E")) +
  theme(legend.position = "top") +
  guides(fill = guide_legend(nrow = 2, byrow = TRUE)) +
  labs(x = NULL, y = NULL, fill = NULL) 

# get missings
p_nas <- nas %>% 
  left_join(select(pdata_institution, var, order)) %>% 
  left_join(labels, by = c("var" = "var_id")) %>% 
  distinct() %>% 
  group_by(label, order) %>% 
  summarise(n = sum(n))

p2 <- p_nas %>% 
  ggplot(aes(y = fct_reorder(label, order), x = n)) +
  geom_col(fill = "grey50", width = .7) +
  labs(x = NULL, y = "# of answers of 'Not applicable' or 'I don't know'") +
  scale_x_continuous(breaks = c(0, 32)) +
  scale_y_discrete(position = "right") +
  hrbrtheme_fixed(grid = "", plot_margin = margin(l = 5)) +
  theme(panel.border = element_rect(fill = NA, colour = "grey80"),
        axis.text.y = element_blank(),
        axis.title.y = element_text( angle = 270))

p1 + 
  theme(plot.margin = margin()) + p2 +
  plot_layout(widths = c(6, 1)) +
  plot_annotation(caption = "n = 198")
```


# Personal view: X47 - X65
"In your own personal opinion, how important should the following research activities be when making promotion decisions?  [Publishing a large number of research articles]"

etc.

```{r}
step1 <- df %>% 
  select(X47:X65) %>% 
  pivot_longer(everything(), names_to = "var", values_to = "val") %>%
  count(var, val)

# remove dont knows and not applicables
nas <- step1 %>% 
  filter(val %in% c("I don't know", "Not applicable"))

pdata <- step1 %>% 
  anti_join(nas) %>% 
  mutate(val = fct_relevel(val, "Very important", "Somewhat important",
                           "Neither important nor unimportant", 
                           "Somewhat unimportant", "Very unimportant")) %>% 
  make_proportion(group = var, var = val, order_string = "\\simportant$")


# get labels
labels <- var_overview %>% 
  filter(var_id %in% paste0("X", 47:65)) %>% 
  mutate(label = str_extract(var_full, "(?<=\\[).*?(?=\\s?\\])"),
         # clean up labels
         label = str_remove(label, "\\(.*"),
         label = str_remove(label, ", as assessed .*")) %>% 
  select(var_id, label)

pdata_individual <- pdata %>% 
  left_join(labels, by = c("var" = "var_id"))
```

```{r}
pdata_individual %>% 
  ungroup() %>% 
  arrange(desc(order), val) %>% 
  mutate(prop = scales::percent(prop, accuracy = .1),
         summary = glue::glue("{n} ({prop})")) %>% 
  select(variable = label, value = val, summary) %>%
  pivot_wider(names_from = value, values_from = summary,
              values_fill = "0 (0.0%)", names_sort = TRUE) %>% 
  knitr::kable()
```


```{r personal-attitudes, fig.width=10, fig.height=7}
p1 <- pdata_individual %>% 
  ggplot(aes(fct_reorder(label, order), prop, fill = val)) +
  geom_chicklet(width = .7) +
  coord_flip() +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = c("#B96FB0", "#F9AEEF", "#E0C47C", "#94D790",
                               "#54984E")) +
  theme(legend.position = "top") +
  guides(fill = guide_legend(nrow = 2, byrow = TRUE)) +
  labs(x = NULL, y = NULL, fill = NULL) 

# get missings
p_nas <- nas %>% 
  full_join(distinct(pdata_individual, var, order)) %>% 
  replace_na(list(n = 0)) %>% 
  left_join(labels, by = c("var" = "var_id")) %>% 
  group_by(label, order) %>% 
  summarise(n = sum(n))

p2 <- p_nas %>% 
  ggplot(aes(y = fct_reorder(label, order), x = n)) +
  geom_col(fill = "grey50", width = .7) +
  labs(x = NULL, y = "# of answers of 'Not applicable' or 'I don't know'") +
  scale_x_continuous(breaks = c(0, 24)) +
  scale_y_discrete(position = "right") +
  hrbrtheme_fixed(grid = "", plot_margin = margin(l = 5)) +
  theme(panel.border = element_rect(fill = NA, colour = "grey80"),
        axis.text.y = element_blank(),
        axis.title.y = element_text( angle = 270))

p1 + 
  theme(plot.margin = margin()) + p2 +
  plot_layout(widths = c(6, 1)) +
  plot_annotation(caption = "n = 198")

```


# Comparison
```{r}
institutional_values <- get_values(df, X23:X41, source = "institutional", 
                                   var_overview)
personal_values <- get_values(df, X47:X65, source = "personal", 
                              var_overview)

institutional_scores <- bootstrap_values(institutional_values)
personal_scores <- bootstrap_values(personal_values)

all_scores <- bind_rows(institutional_scores, personal_scores)
all_scores

# compute differences
differences <- all_scores %>% 
  select(label, Mean, source) %>% 
  pivot_wider(names_from = source, values_from = Mean) %>% 
  mutate(diff = personal - institutional) 

differences %>% 
  rename(Question = label) %>% 
  arrange(diff) %>% 
  mutate(across(where(is.numeric), ~round(.x, digits = 2))) %>% 
  knitr::kable()
```


```{r}
final_scores <- all_scores %>% 
  left_join(differences) %>% 
  select(-institutional, -personal)

final_scores
```

```{r comparison, fig.width=9, fig.height=8}
dodge_width <- .2

custom_blue <- "#3792BD"
yellow <- "#E0C47C"
# "#F9AEEF", "#E0C47C", "#94D790",

bigger_text_size <- 15

pdata <- final_scores %>% 
  mutate(source = recode(source, personal = "Personal view", 
                         institutional = "Perceived institutional view"))
comparison <- pdata %>% 
  ggplot(aes(Mean, fct_rev(fct_reorder(str_wrap(label, 40), diff)))) +
  geom_linerange(aes(xmin = Lower, xmax = Upper, group = fct_rev(source)),
                 position = position_dodge(width = dodge_width),
                 colour = "grey60") +
  geom_point(aes(colour = fct_rev(source)), size = 2.6,
             position = position_dodge(width = dodge_width)) +
  five_point_scale() +
  scale_colour_manual(values = c(
    `Personal view` =  yellow, #"#B96FB0",
    `Perceived institutional view` = custom_blue #"#54984E"
  )) +
  labs(y = NULL, colour = NULL, x = NULL) +
  theme(legend.position = "top", plot.margin = margin(), 
        legend.text = element_text(size = bigger_text_size),
        axis.text.y = element_text(size = bigger_text_size),
        axis.text.x = element_text(size = bigger_text_size))
comparison
```

# Combine them
```{r comparison-enhanced, fig.height=11, fig.width=12}
arrows <- png::readPNG(here::here("analysis-notebooks/comparison-addition.PNG"),
                       native = TRUE)
comparison + wrap_elements(panel = arrows) +
  plot_layout(widths = c(5, 1))
```

# Correlational analysis
Wondering: are correlations within individuals similar to above picture, or is 
this another angle?

```{r}
cor_data <- bind_rows(personal_values, institutional_values) %>% 
  select(-val) %>% 
  pivot_wider(names_from = "source", values_from = "num_val") %>% 
  group_by(label)

cor_data %>% 
  summarise(correlation = cor(personal, institutional, use = "pairwise",
                              method = "spearman")) %>% 
  arrange(correlation) %>% 
  mutate(correlation = round(correlation, 3))
```

```{r}
conf_ints <- cor_data %>% 
  summarise(res = list(cor.test(personal, institutional, conf.level = .995))) %>% 
  mutate(cor = map_dbl(res, pluck, "estimate"),
         conf_int = map(res, pluck, "conf.int"),
         lower = map_dbl(conf_int, pluck, 1),
         upper = map_dbl(conf_int, pluck, 2)) %>% 
  select(label, cor, lower, upper) %>% 
  arrange(cor)
conf_ints
```

```{r corr-comparison, fig.width=8, fig.height=7}
conf_ints %>% 
  ggplot(aes(cor, fct_reorder(label, cor))) +
  geom_linerange(aes(xmin = lower, xmax = upper)) +
  geom_point(size = 2, colour = custom_blue) +
  labs(x = "Correlation between personal and perceived institutional view",
       y = NULL)
```

There is big uncertainty in the estimates, and the linear approach inherent with
correlations might not be the right model. Following this approach,
it seems that for some 
questions personal and institutional views are more aligned than for others.
This does not follow the exact same pattern as with the above comparison.

To explore a little further how these values come about.

Now do mean differences instead of difference of means as in original analysis.

```{r}
cor_data %>% 
  summarise(diff = mean(personal - institutional, na.rm = TRUE)) %>% 
  arrange(diff) %>% 
  mutate(diff = round(diff, 3)) %>% 
  knitr::kable()
```

This is not identical but very close to our original figure.


```{r}
cor_data %>% 
  filter(str_detect(label, "Openly.*")) %>% 
  tabyl(personal, institutional) %>% 
  custom_adorns() %>% 
  knitr::kable()
```

```{r}
cor_data %>% 
  filter(str_detect(label, "highly regarded")) %>% 
  tabyl(personal, institutional) %>% 
  custom_adorns() %>% 
  knitr::kable()
```

```{r}
cor_data %>% 
  filter(str_detect(label, "code")) %>% 
  tabyl(personal, institutional) %>% 
  custom_adorns() %>% 
  knitr::kable()
```

# Summarise indicators into groups
```{r}
all_Values <- bind_rows(institutional_values, personal_values) %>% 
  mutate(label = str_remove(label, "\\s$")) %>% 
  left_join(expanded_labels) %>% 
  rename(id = X1)
all_Values
```

```{r}
scores_by_individual <- all_Values %>% 
  group_by(id, group, source) %>% 
  summarise(score = mean(num_val))
```

```{r}
demographics <- df %>% 
  select(id = X1, disciplines_recoded_wos, acad_age = X87, gender = X84,
         acad_rol = X85) %>% 
  mutate(# fix two cases where data was entered incorrectly
         acad_age = case_when(acad_age == 19999 ~ 1999,
                              acad_age == 84 ~ 1984,
                              TRUE ~ acad_age),
         acad_age = 2021 - acad_age)
```

```{r age_histogram}
demographics %>% 
  ggplot(aes(acad_age)) +
  geom_histogram()
```



```{r}
scores_by_individual <- scores_by_individual %>% 
  left_join(demographics)
scores_by_individual
```

## by disciplines
```{r scores-by-discipline, fig.height=9, fig.width=8}
scores_by_individual %>% 
  mutate(group = str_wrap(group, width = 12)) %>% 
  filter(!is.na(disciplines_recoded_wos)) %>% 
  ggplot(aes(score, disciplines_recoded_wos)) +
  geom_boxplot(width = .7, outlier.alpha = 0, notch = TRUE, 
               fill = custom_blue) +
  #geom_jitter(height = .1, width = .01, colour = custom_blue, alpha = .5) +
  five_point_scale(compact = TRUE) +
  facet_grid(rows = vars(group), cols = vars(source)) +
  labs(y = NULL) +
  theme(panel.spacing.x = unit(4, "lines"))
```

No substantive differences. Sample size is too small to allow drawing 
conclusions here, since precisions would need to be much higher, given that we
are conducting a large number of comparisons at once. 

## by gender
```{r scores-by-gender, fig.height=8, fig.width=8}
scores_by_individual %>% 
  mutate(group = str_wrap(group, width = 12)) %>% 
  filter(!is.na(gender), gender != "Prefer not to say") %>% 
  ggplot(aes(score, gender)) +
  geom_boxplot(width = .7, outlier.alpha = 0, notch = TRUE) +
  geom_jitter(height = .05, width = .01, colour = custom_blue, alpha = .2) +
  facet_grid(rows = vars(group), cols = vars(source)) +
  five_point_scale(compact = TRUE) +
  theme(panel.spacing.x = unit(4, "lines")) +
  labs(y = NULL, x = "Aggregated score across indicator group")
```

There are no differences regarding the institutional side. Regarding personal
views, women tend to give higher importance to community activities and
societal and economic impact than men, all other aspects being similar.

This finding should be backed up by checking the gender distribution across
disciplines. Life sci & Biomed also has a higher score in these two items, 
although only slightly.


### Gender by discipline
```{r, message=FALSE}
library(tidylog)
```


```{r}
tab <- demographics %>% 
  filter(!is.na(disciplines_recoded_wos), gender != "Prefer not to say") %>% 
  tabyl(disciplines_recoded_wos, gender)

tab %>% 
  chisq.test()

tab %>% 
  custom_adorns() %>% 
  knitr::kable()
```

Women are much better represented in Life Sci & Biomed.

It would therefore seem, that the higher higher importance to community
activities and societal and economic impact can still be attributed to gender,
and not discipline.

In causal terms, gender would have an impact on scores, as well as on discipline,
but discipline only on scores, and not on gender.

To assess the total causal effect of gender, we therefore do not need to control
for gender. For the partial effect of gender alone, we would need to control for
discipline.

```{r, include=FALSE}
options("tidylog.display" = list())
```


### scores by gender continued

```{r}
model_data <- scores_by_individual %>% 
  filter(!is.na(gender), gender != "Prefer not to say") %>% 
  filter(source == "personal", group == "Societal & economic impact")

m <- aov(score ~ gender, data = model_data)
summary(m)

m2 <- aov(score ~ gender + disciplines_recoded_wos, data = model_data)
summary(m2)
```

```{r}
model_data <- scores_by_individual %>% 
  filter(!is.na(gender), gender != "Prefer not to say") %>% 
  filter(source == "personal", group == "Community activities")

m <- aov(score ~ gender, data = model_data)
summary(m)

m2 <- aov(score ~ gender + disciplines_recoded_wos, data = model_data)
summary(m2)
```

In both cases, differences between genders regarding the personal view on
community activities and societal & economic impact are not statistically 
significant. This does not change (in either direction) when also controlling
for gender. Overall, however, this method is not well suited to the data, given
that the data are in the interval [0, 1], but the method (ANOVA) assumes 
normally distributed error terms, which is not the case here. 


## by country
```{r scores-by-country, fig.height=8, fig.width=8, eval=FALSE}
scores_by_individual %>% 
  ungroup() %>% 
  mutate(country_lumped = fct_lump_n(country, 3)) %>% 
  mutate(group = str_wrap(group, width = 12)) %>% 
  ggplot(aes(score, country_lumped)) +
  geom_boxplot(width = .7, outlier.alpha = 0, notch = TRUE) +
  geom_jitter(height = .05, width = .01, colour = custom_blue, alpha = .2) +
  facet_grid(rows = vars(group), cols = vars(source)) +
  five_point_scale(compact = TRUE) +
  theme(panel.spacing.x = unit(4, "lines")) +
  labs(y = NULL, x = "Aggregated score across indicator group")
```

This comparison is again fraught with difficulties, since there are numerous 
pairs which can be compared. The main difference that stands out is the 
relatively low perceived institutional relevance that respondents from the USA
report for societal & economic impact. It is hard to draw any further 
conclusions, given the small sample size.

We can test this specific table, but would need to reduce the significance
threshold at least by the factor 10 (5% -> 0.5%).

```{r, eval=FALSE}
model_data <- scores_by_individual %>% 
  ungroup() %>% 
  mutate(country_lumped = fct_lump_n(country, 3)) %>% 
  filter(source == "institutional", group == "Societal & economic impact")

m <- aov(score ~ country_lumped, data = model_data)
summary(m)
```

As such, the p-value is not small enough to meet this threshold. So the results
are still not strong enough to discard the assumption that all means in this
group might be similar.

## Academic age
```{r}
scores_by_individual %>% 
  group_by(source, group) %>% 
  summarise(res = list(cor.test(acad_age, score, conf.level = .995))) %>% 
  mutate(cor = map_dbl(res, pluck, "estimate"),
         conf_int = map(res, pluck, "conf.int"),
         lower = map_dbl(conf_int, pluck, 1),
         upper = map_dbl(conf_int, pluck, 2)) %>% 
  select(source, group, cor, lower, upper) %>% 
  arrange(source, desc(cor)) %>% 
  mutate(across(where(is.numeric), round, digits = 2)) %>% 
  knitr::kable()
```

There are no substantive correlations. The only one which could be claimed as
being weak, is in the personal view on alternative academic impact. 

```{r score-vs-acad-age, fig.height=15, fig.width=10}
scores_by_individual %>% 
  ggplot(aes(acad_age, score)) +
  geom_jitter(height = .1, width = .5, alpha = .5) +
  geom_smooth(colour = custom_blue) +
  facet_grid(rows = vars(group),
             cols = vars(source)) +
  scale_y_continuous(
      breaks = c(1, 3, 5),
      labels = c("Very important", "Neither/nor", "Very unimportant")
  ) +
  labs(x = "Academic age", y = NULL)
```

The low linear relationship is confirmed via the plot. However, there seems to
be some inverse U-shaped pattern, where older and younger respondents give 
higher weight to some of the concepts, while middle aged respondents (academic
age of 15-30 years) give them lower weight. However, these trends are not 
present in all cases and overall not very strong.
