---
title: "Opinion vs practice"
author: "Thomas Klebel"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggchicklet)
library(patchwork)
library(janitor)
library(tidylog)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, dpi = 300)

extrafont::loadfonts(device = "win")

theme_set(hrbrthemes::theme_ipsum_rc(base_family = "Hind"))

df <- targets::tar_read(shareable_data)
var_overview <- targets::tar_read(var_overview)

opinion_levels <- c("Very important", "Somewhat important",
                           "Neither important nor unimportant", 
                           "Somewhat unimportant", "Very unimportant",
                           "I don't know", "Not applicable")

custom_blue <- "#3792BD"
```


# Code sharing - who is missing?
Characterise respondents that answer "Not applicable" to code sharing.

```{r}
# X53 is personal view on code sharing
df %>% 
  mutate(X53 = factor(X53, levels = opinion_levels)) %>% 
  tabyl(disciplines_recoded_wos, X53) %>% 
  custom_adorns() %>% 
  knitr::kable()
```

The answers "I don't know" and "Not applicable" are clearly over-represented 
among SSH in the
question on the personal relevance of code sharing.


# Relevance of impact beyond academia vs institutional view

# Open practice vs opinion
## OA publishing
```{r}
# OA publishing
# X68 = pubs total
# X69 = pubs OA
# X51 = personal opinion on OA
# X27 = institutional opinion on OA

oa_practice <- df %>% 
  select(X27, X51, X68, X69) %>% 
  mutate(OA_rate = X69/X68,
         X51 = factor(X51, levels = opinion_levels),
         X27 = factor(X27, levels = opinion_levels))
oa_practice
```

```{r}
ggplot(oa_practice, aes(OA_rate)) +
  geom_histogram(bins = 20)
```
Values that should not exist, i.e. more OA articles than total articles.
-> Removing those two cases

```{r}
oa_practice <- oa_practice %>% 
  filter(OA_rate <= 1 | is.na(OA_rate))
```



```{r OA-views, fig.width=8, fig.height=8}
set.seed(123)
oa_practice %>% 
  pivot_longer(c(X27, X51), names_to = "variable") %>% 
  mutate(variable_rec = recode(variable, X27 = "Perceived institutional view",
                               X51 = "Personal view")) %>% 
  ggplot(aes(OA_rate, fct_rev(value))) +
  geom_boxplot(width = .5, outlier.alpha = 0) +
  geom_jitter(height = .1, width = .01, colour = custom_blue, alpha = .5) +
  facet_wrap(vars(variable_rec), nrow = 2) +
  scale_x_continuous(labels = scales::percent) +
  labs(x = "% of publications which are OA", y = "Importance of OA publishing")
```
General trend holds: if respondents think OA is more important, they also have 
more OA publications, and vice versa. 

More strict tests for personal view:
```{r}
m1 <- aov(OA_rate ~ X51, data = oa_practice)
```
```{r}
summary(m1)
```

```{r}
pairwise.t.test(oa_practice$OA_rate, oa_practice$X51, p.adjust.method = "BH")
```

Some group differences are "statistically significant". But this also comes down
to the method used for the correction. Overall, it seems reasonable to state 
that higher OA share is related to stronger opinion in favour.

```{r}
# effect size
eta <- DescTools::EtaSq(m1)[1]
eta
```

Not versed with these values, would need to look into how specifically interpret.

## Open data
```{r}
# Data sharing
# X72 = pubs total
# X73 = pubs OA
# X52 = personal opinion on OD
# X28 = institutional opinion on OD

od_practice <- df %>% 
  select(X28, X52, X72, X73) %>% 
  mutate(OD_rate = X73/X72,
         X52 = factor(X52, levels = opinion_levels),
         X28 = factor(X28, levels = opinion_levels))
od_practice
```

```{r}
ggplot(od_practice, aes(OD_rate)) +
  geom_histogram(bins = 20)
```
Values that should not exist, i.e. more open datasets than total datasets
-> Removing this case.

```{r}
od_practice <- od_practice %>% 
  filter(OD_rate <= 1 | is.na(OD_rate)) %>% 
  filter(!is.na(OD_rate))
```

```{r OD-views, fig.width=8, fig.height=8}
set.seed(123)
od_practice %>% 
  pivot_longer(c(X28, X52), names_to = "variable") %>% 
  mutate(variable_rec = recode(variable, X28 = "Perceived institutional view",
                               X52 = "Personal view")) %>% 
  ggplot(aes(OD_rate, fct_rev(value))) +
  geom_boxplot(width = .5, outlier.alpha = 0) +
  geom_jitter(height = .1, width = .01, colour = custom_blue, alpha = .5) +
  facet_wrap(vars(variable_rec), nrow = 2) +
  scale_x_continuous(labels = scales::percent) +
  labs(x = "% of datasets which are open", y = "Importance of OD sharing")
```

```{r}
m2 <- aov(OD_rate ~ X28  + X52, data = od_practice)
summary(m2)
```
Differences are not statistically significant. However, this model is likely not
suitable to the data at hand (zero and one inflation, general structure of 
response in interval [0, 1], etc.)

A better alternative is to look at chisquare tables. The following table is
for the institutional view.
```{r}
inst_table <- od_practice %>% 
  filter(!(X28 %in% c("Not applicable", "I don't know"))) %>% 
  mutate(X28 = fct_drop(X28)) %>% 
  mutate(od_cats = cut_interval(OD_rate, 4) %>% fct_rev()) %>% 
  tabyl(od_cats, X28)

chisq.test(inst_table)  

inst_table %>% 
  custom_adorns() %>% 
  knitr::kable()
```

```{r}
personal_table <- od_practice %>% 
  filter(!(X52 %in% c("Not applicable", "I don't know"))) %>% 
  mutate(X52 = fct_drop(X52)) %>% 
  mutate(od_cats = cut_interval(OD_rate, 4) %>% fct_rev()) %>% 
  tabyl(od_cats, X52)

chisq.test(personal_table)  

personal_table %>% 
  custom_adorns() %>% 
  knitr::kable()
```

Based on these tables:

- There seems to be no association between personal views on OD as a promotion
criterion and actual OD practice.
- There seems to be some association between perceived institutional view on OD
as a promotion criterion and actual OD practice. 
- This is contrary to the conclusions that one might glimpse from comparing 
medians. Why?

# Influence of policies on choice of venue
Question: In the last three years, my choice of publication venue (journal, book publisher, conference, etc.) was influenced by the promotion criteria of my university.

With "other" values
```{r policy-venue, fig.width=6, fig.height=4}
df %>% 
  select(X71) %>% 
  mutate(X71 = fct_relevel(X71,
                           "Very often", "Often", "Neither often nor rarely",
                           "Rarely", "Very rarely") %>% fct_rev()) %>% 
  plot_bar(X71, reorder = FALSE, nudge_y = .01)
```

Without
```{r policy-venue-2, fig.width=6, fig.height=2.5}
df %>% 
  select(X71) %>% 
  filter(!(X71 %in% c("I don't know", "Does not apply"))) %>% 
  mutate(X71 = fct_relevel(X71,
                           "Very often", "Often", "Neither often nor rarely",
                           "Rarely", "Very rarely") %>% fct_rev()) %>% 
  plot_bar(X71, reorder = FALSE, nudge_y = .01)
```
This version has 178 cases.
