---
title: "Importance for research vs opinions"
author: "Thomas Klebel"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggchicklet)
library(patchwork)
library(janitor)
library(ca)
library(corrplot)

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, dpi = 300)

extrafont::loadfonts(device = "win")

theme_set(hrbrthemes::theme_ipsum_rc(base_family = "Hind"))

df <- targets::tar_read(shareable_data)
var_overview <- targets::tar_read(var_overview)

opinion_levels <- c("Very important", "Somewhat important",
                           "Neither important nor unimportant", 
                           "Somewhat unimportant", "Very unimportant",
                           "I don't know", "Not applicable")

custom_blue <- "#3792BD"
```

Do two approaches:

1. Similar to the general comparison plot, comparing aggregate levels
2. Correspondence analysis

```{r}
# How important to engage with
# X78 = public
# X80 = industry
# X82 = Policy

# Institutional policy
# X30  = public
# X31  = industry
# X33 = policy

core_data <- df %>% 
  select(inst_public = X30, inst_industry = X31, inst_policy = X33,
         imp_public = X78, imp_industry = X80, imp_policy = X82)

core_data %>% 
  head(10) %>% 
  knitr::kable()
```

```{r}
long_data <- core_data %>% 
  mutate(across(.fns = get_numeric_val)) %>% 
  pivot_longer(everything(), names_to = c("source", "type"),
               names_pattern = "(.*)_(.*)") %>% 
  mutate(source = recode(source, inst = "Perceived institutional view", 
                         imp = "Importance for success of research"))
```


```{r}
bootstrapped <- long_data %>% 
  group_by(source, type) %>% 
  summarise(res = list(Hmisc::smean.cl.boot(value))) %>%
  unnest_wider(res)
```
```{r importance-for-research-vs-policy}
dodge_width <- .2
yellow <- "#E0C47C"

bootstrapped %>% 
  ggplot(aes(Mean, type, colour = source)) +
  geom_linerange(aes(xmin = Lower, xmax = Upper, group = fct_rev(source)),
                 position = position_dodge(width = dodge_width),
                 colour = "grey60") +
  geom_point(aes(colour = fct_rev(source)), size = 2.6,
             position = position_dodge(width = dodge_width)) +
  five_point_scale() +
    scale_colour_manual(values = c(
    `Importance for success of research` =  yellow, #"#B96FB0",
    `Perceived institutional view` = custom_blue #"#54984E"
  )) +
  labs(y = NULL, colour = NULL, x = NULL) +
  theme(legend.position = "top")
```

Aggregate levels are very similar. Biggest dis-alignment with industry, although
differences still quite close and within confidence intervals for the means.

## Via correspondence analysis
```{r}
# simplify for plotting
make_names_simple <- function(x, keep_NA = TRUE) {
  if (keep_NA) {
    case_when(
      x == "Very important" ~ "++",
      x == "Important" ~ "+",
      x == "Somewhat important" ~ "+",
      x == "Neither important nor unimportant" ~ "=",
      x == "Unimportant" ~ "-",
      x == "Somewhat unimportant" ~ "-",
      x == "Very unimportant" ~ "--",
      x == "I don't know" ~ "?",
      x == "Not applicable" ~ "NA"
    )
  } else {
    case_when(
      x == "Very important" ~ "++",
      x == "Important" ~ "+",
      x == "Somewhat important" ~ "+",
      x == "Neither important nor unimportant" ~ "=",
      x == "Unimportant" ~ "-",
      x == "Somewhat unimportant" ~ "-",
      x == "Very unimportant" ~ "--",
      x == "I don't know" ~ "?"
    )
  }

}
```

```{r compute-mca}
mca_model <- core_data %>%
  mutate(across(everything(), make_names_simple)) %>% 
  ca::mjca()
```


```{r}
prettify <- list(
  theme(legend.position = "top",
        axis.title.x = element_text(size = rel(1.5)),
        axis.title.y = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.2)),
        legend.text = element_text(size = rel(1.1)))
  #scale_color_manual(values = scale_spectral) 
)
```


```{r mca-bare, fig.width=15, fig.height=15}
# scale_short <- c("Indicator present" = "#3588BD", 
#                     "Indicator not present" = "#C26574")

mca_model %>%
  plot_ca(font_size = 5, show.legend = TRUE) +
  coord_fixed() +
  prettify 
```

Second dimension is mainly NAs, so removing.

```{r re-compute-mca}
m2 <- core_data %>%
  mutate(across(everything(), make_names_simple, keep_NA = FALSE)) %>% 
  ca::mjca()
```


```{r mca-2, fig.width=15, fig.height=15}
m2 %>%
  plot_ca(font_size = 5, keep_labels = TRUE) +
  coord_fixed() +
  prettify 
```

Broadly speaking: categories agree to each other, all of them are similar.
Only exception: perceived institutional policies of complete unimportance are a 
little removed from the rest - level of unimportance is higher for these three
than for the importance to own research.

The general pattern is a typical horseshoe-patter and of no substantive 
relevance.

A correlation analysis likely might bring out more subtle differences.


## Correlation analysis
```{r}
cor_base <- core_data %>% 
  mutate(across(.fns = get_numeric_val))

cor_matrix <- cor_base %>% 
  cor(use = "pairwise.complete.obs", method = "spearman")
cor_matrix %>% 
  knitr::kable()
```

```{r}
plot_correlation <- function(cor_matrix, cluster = TRUE) {
  # code from http://www.sthda.com/english/wiki/visualize-correlation-matrix-using-correlogram
  # col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
  
  col <- colorRampPalette(c(yellow, "#FFFFFF", "#0880AB"))
  order <- ifelse(cluster, "hclust", "original")
  
  corrplot::corrplot(
    cor_matrix, method = "color", col = col(200),  
    type = "upper", order = order, 
    addCoef.col = "black", # Add coefficient of correlation
    tl.col = "black", tl.srt = 45, #Text label color and rotation
    # hide correlation coefficient on the principal diagonal
    diag = FALSE 
  )
}
```


```{r correlation}
plot_correlation(cor_matrix, cluster = FALSE)
```
Here, "inst" denotes the perceived institutional policy, and "imp" denotes
the relevance to the respondents research. 

Correlations in the upper right square (3x3), which shows the relationships 
between perceived institutional policies and the relevance to research, are
generally low to moderate. 

The correlations between the three types, comparing relevance to research and
perceived institutional policy, are .39 (public), .32 (industry), and
.4 (policy). Thus, there seems to be moderate alignment between importance for
researchers and perceived institutional policies.

However, it is unclear how much alignment could be expected, and therefore,
whether this finding is of any substantive interest. 

All three key correlations are statistically significant (after correction
for multiple comparisons via the approach developed by Benhamini & Hochberg 
(1995))

```{r correlation-significance}
p_vals <- corrplot::cor.mtest(cor_base)$p
adj_p_vals <- p.adjust(p_vals, method = "fdr") %>% 
  matrix(nrow = 6) 

colnames(adj_p_vals) <- colnames(p_vals)
rownames(adj_p_vals) <- rownames(p_vals)

col <- colorRampPalette(c(yellow, "#FFFFFF", "#0880AB"))
corrplot::corrplot(
  cor_matrix, method = "color",  col = col(200),
  type = "upper", p.mat = adj_p_vals, sig.level = .05,
  addCoef.col = "black", # Add coefficient of correlation
  tl.col = "black", tl.srt = 45, #Text label color and rotation
  # hide correlation coefficient on the principal diagonal
  diag = FALSE 
)
```

# Refs
Benjamini, Y., and Hochberg, Y. (1995). Controlling the false discovery rate: a practical and powerful approach to multiple testing. Journal of the Royal Statistical Society Series B, 57, 289–300. doi: 10.1111/j.2517-6161.1995.tb02031.x. https://www.jstor.org/stable/2346101.

